Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by Galaxy Cluster Abell 2744

### 2015-05-04 TABLE/magnifications2.tex
fixed shuffled values in Table 4

@@

Sharon(v2)     & 17 &  60 & 2 & 14 &  \citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model. Includes cosmological parameter variations in uncertainty estimates.\\
CATS(v1sw)     & 24 &  67 & 3 & 12 &  \citealt{Richard:2014} &  CATS team LENSTOOL parametric model with both strong and weak lensing constraints.\\
GLAFIC         & 15 &  47 & 3 & 11 &  \citealt{Ishigaki:2015} & Parametric strong-lensing model using v1.0 of the {\tt GLAFIC} code.\tablenotemark{h} \\

@@

@@

Bradac(v2)     & 10 &  40 & 2 & 8  &  \citealt{Wang:2015} & Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging. Errors from bootstrap resampling only strong-lensing constraints.\\
Williams       & 16 &  56 & 2 & 14 &  HFF & {\tt GRALE}\tablenotemark{j} : Free-form strong-lensing model using a genetic algorithm.  \\
Merten         & 25 &  72 & 7 & 18 &  HFF; \citealt{Merten:2011} &  {\tt SaWLENS},\tablenotemark{k} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\

>>>>

CATS(v1sw)     & 17 &  60 & 2 & 14 &  \citealt{Richard:2014} &  CATS team LENSTOOL parametric model with both strong and weak lensing constraints.\\
GLAFIC         & 24 &  67 & 3 & 12 &  \citealt{Ishigaki:2015} & Parametric strong-lensing model using v1.0 of the {\tt GLAFIC} code.\tablenotemark{h} \\

@@

Sharon(v2)     & 15 &  47 & 3 & 11 &  \citealt{Johnson:2014} & LENSTOOL parametric, strong-lensing based model. Includes cosmological parameter variations in uncertainty estimates.\\

@@

Merten         & 16 &  56 & 2 & 14 &  HFF; \citealt{Merten:2011} &  {\tt SaWLENS},\tablenotemark{k} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
Williams       & 10 &  40 & 2 & 8  &  HFF & {\tt GRALE}\tablenotemark{j} : Free-form strong-lensing model using a genetic algorithm.  \\

@@

Bradac(v2)     & 25 &  72 & 7 & 18 &  \citealt{Wang:2015} & Updated version of the {\tt SWUnited} model with new strong-lensing constraints from HFF imaging. Errors from bootstrap resampling only strong-lensing constraints.\\

### 2015-05-04 snTomas.tex
fixed shuffled values in Table 4

A promising avenue for exploring the origins of systematic biases in
cluster lens models is through the use of simulated lensing data.  One
can start with very deep high-resolution multi-band imaging on an
unlensed field that has a fairly complete spectroscopic redshift
catalog, such as the Hubble Ultra Deep Field.  Then a simulated galaxy
cluster is placed in the field, and the background galaxies are
distorted into arcs and multiple images using a well-defined lensing
prescription.  The artificially lensed images can then be distributed
to lens modeling teams who attempt to reconstruct the (known) mass
profile of the simulated cluster.  This exercise has recently been
pursued with a set of synthetic clusters similar to those observed in
the HFF program (Meneghetti et al. in prep).  Preliminary analysis of
this simulation comparison suggests that magnifications tend to be
overestimated for sources that lie outside the strong-lensing region
along the minor axis direction of \changeR{simulated clusters that are
very elongated, similar to Abell 2744. This finding would be
consistent with a recent lens model comparison on 25 real clusters
from the CLASH program \citep{Zitrin:2015}.} Our analysis of
SN \tomas\ here indicates that such simulation efforts \changeR{and
head-to-head lens model comparisons} will be an important step for
moving toward precision science with cluster-lensed sources.

>>>>

A promising avenue for exploring the origins of systematic biases in
cluster lens models is through the use of simulated lensing data.  One
can start with very deep high-resolution multi-band imaging on an
unlensed field that has a fairly complete spectroscopic redshift
catalog, such as the Hubble Ultra Deep Field.  Then a simulated galaxy
cluster is placed in the field, and the background galaxies are
distorted into arcs and multiple images using a well-defined lensing
prescription.  The artificially lensed images can then be distributed
to lens modeling teams who attempt to reconstruct the (known) mass
profile of the simulated cluster.  This exercise has recently been
pursued with a set of synthetic clusters similar to those observed in
the HFF program (Meneghetti et al. in prep), \changeP{using techniques
similar to \citet{Meneghetti:2010,Meneghetti:2014}}.  Preliminary
analysis of this simulation comparison suggests that
magnifications \change{can} be systematically overestimated for
sources that lie outside the strong-lensing region along the minor
axis direction of \changeR{ simulated clusters that are very
elongated, similar to Abell 2744.}  \changeP{This indicates that some
lens models significantly underestimate the ellipticity of the mass
distribution on large scales for those simulated clusters, which is
consistent with a recent lens model comparison on 25 real clusters
from the CLASH program \citep{Zitrin:2015}.} Our analysis of
SN \tomas\ here indicates that such simulation efforts \changeR{and
head-to-head lens model comparisons} will be an important step for
moving toward precision science with cluster-lensed sources.
